\LARGE \bf Multi-dimensional Optimization of Gasoline-fueled Variable Pitch Multirotor Aircraft

### 2016-03-24 paper.tex
more methods stuff

There are many commercially available parts for a gas quad, including motors

@@

@@

\begin{itemize}
	\item{Analysis models}
	\begin{itemize}
		\item{Empirical engine models}
		\item{Rotor Aerodynamic models}
	\end{itemize}
	\item{Simplifications - since we are stupid}
\end{itemize}

\section{OPTIMIZATION}
Setup the formal optimization problem
\begin{equation}
min. \quad f\of{x} = -flightTime\of{x}
\label{eq:objective}
\end{equation}
\begin{equation}
w.r.t. \quad x = [variables]^T
\label{eq:vars}
\end{equation}
\begin{equation}
s.t. \quad cons\of{x} <= 0 
\label{eq:constrants}
\end{equation}

>>>>

There are many commercially available parts for a gas quad, including engines and variable pitch helicopter propellers.

@@

Because the quad is going to be build using commercially available off the shell parts the optimization must be closely based on reality.  Ultimately that means we only can pick the size of engine that we are going to use.  All the other data about the engine (mass, maximum power, etc.) have to be a function of displacement size.  We collected data about popular two stroke RC aircraft engines from several sources to produce the below plots.

\begin{figurehere}
	\includegraphics[width=0.5\textwidth]{mass.png}
	\caption{Stand in figure showing the data used to obtain the empirical based surrogate model of engine mass as a function of displacement size.}
		\label{fig:mass}
\end{figurehere}

\begin{figurehere}
	\includegraphics[width=0.5\textwidth]{max_power.png}
	\caption{Stand in figure showing the data used to obtain the empirical based surrogate model of engine maximum power as a function of displacement size.}
		\label{fig:power}
\end{figurehere}

The engine efficiency (friction and heat transfer losses), however, is a function of power capability of the engine (max power) and the power engine is required to produce.  For this we will need a better model.  \textit{We are still working on this. Since efficiency numbers for RC engines aren't publicly available, we need a scientific model.  For now we just assume a constant efficiency. We plan to work on this in the future.}

@@

\section{OPTIMIZATION}

Setup the formal optimization problem
\begin{equation}
min. \quad f\of{x} = -flightTime\of{x}
\label{eq:objective}
\end{equation}
\begin{equation}
w.r.t. \quad x = [variables]^T
\label{eq:vars}
\end{equation}
\begin{equation}
s.t. \quad cons\of{x} <= 0 
\label{eq:constrants}
\end{equation}
